Efficient pedigree recording for fast population genetics simulation

### 2017-11-20 forwards_paper.tex
remove xtra char

\jda{Is this the right place for this paragraph? should it maybe be integrated
	with graf beginning 'Modern computing' above?}
\plr{this paragraph is supposed to cite the fwds time simulation methods we need to - @molpopgen fix this up?}
Forwards-time population genetics simulations are growing in importance,
as the genome-wide impacts of hitchhiking and background selection are more widely appreciated.
For instance, \citet{harris2016genetic} used SLiM \citep{slim`} to simulate tens of thousands of human exomes
to assess the impact of genetic load and Neanderthal introgression on human genetic diversity.
This is roughly state-of-the-art
-- the fastest simulation frameworks such as SLiM and fwdpp \citep{fwdpp}
can ``only'' simulate tens of megabases of sequence in tens of thousands of individuals
for tens of thousands of generations.
This is still substantially short of whole genomes (hundreds to thousands of megabases)
for many biological population sizes of interest
(e.g., millions for a restricted population of mosquitos).
Achieving these sizes will likely require parallelization \citep{lawrie2017accelerating}.
The general idea of storing genealogical information to speed up simulations is not new --
it was entirely implemented in AnA-FiTS \citep{aberer2013rapid}, for instance --
but this program did not implement the critical step of discarding irrelevant genealogical information.
A similar but more limited method for discarding this information does appear in \citet{padhukasahasram2008exploring}.

>>>>

\jda{Is this the right place for this paragraph? should it maybe be integrated
	with graf beginning 'Modern computing' above?}
\plr{this paragraph is supposed to cite the fwds time simulation methods we need to - @molpopgen fix this up?}
Forwards-time population genetics simulations are growing in importance,
as the genome-wide impacts of hitchhiking and background selection are more widely appreciated.
For instance, \citet{harris2016genetic} used SLiM \citep{slim} to simulate tens of thousands of human exomes
to assess the impact of genetic load and Neanderthal introgression on human genetic diversity.
This is roughly state-of-the-art
-- the fastest simulation frameworks such as SLiM and fwdpp \citep{fwdpp}
can ``only'' simulate tens of megabases of sequence in tens of thousands of individuals
for tens of thousands of generations.
This is still substantially short of whole genomes (hundreds to thousands of megabases)
for many biological population sizes of interest
(e.g., millions for a restricted population of mosquitos).
Achieving these sizes will likely require parallelization \citep{lawrie2017accelerating}.
The general idea of storing genealogical information to speed up simulations is not new --
it was entirely implemented in AnA-FiTS \citep{aberer2013rapid}, for instance --
but this program did not implement the critical step of discarding irrelevant genealogical information.
A similar but more limited method for discarding this information does appear in \citet{padhukasahasram2008exploring}.
